---
title: "ANA 515 Assignment 2"
author: "Sparsh Kathuria"
date: '2022-06-19'
output: 
  html_document:
    theme: 
      bootswatch: minty
---

```{r setup, echo = TRUE}
# Install libraries
library(tidyverse)
library(knitr)
library(rmarkdown)
```

This data I chose includes movie ratings on Fandango and the data was pulled on August 24, 2015. The data is in the form of csv and contains every film that has a Rotten Tomatoes rating, a RT User rating, a Metacritic score, a Metacritic User score, and IMDb score, and at least 30 fan reviews on Fandango. It has information about both Rotten Tomatoes score and Fandango rating, to provide a good comparison of ratings between the two and determine if the ratings at Fandango are suspicious or not.
The dataset has 147 rows and 21 columns.
If we think about it, the initial few weeks of the movies being released, the change in IMDB score or rotten tomatoes would be significant, maybe once every hour however as the movie becomes older, there is not a lot of changes in it. 
The data being pulled is in a .csv format.It is delimited by comma.


Reading Data into R

```{r , echo = TRUE}
#Import data from url
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/fandango/fandango_scrape.csv"
df <- read_csv(url)
print(colnames(df))
```

Cleaning the Data

```{r , echo = TRUE}
# Filter data for votes greater than 10000
highvotes<-filter(df, VOTES >= 10000)
```

Characterstics of the data

```{r , echo = TRUE}
#number of rows in df
df_nrow <- nrow(highvotes)
df_ncol <- ncol(highvotes)
```

This dataframe has `r df_nrow` rows and `r df_ncol` columns. The names of the columns and a brief description of each are in the table below:

```{r , echo = TRUE}
# declare empty dataframe
desc <- data.frame(matrix(ncol = 2, nrow = 4))

# get column names
cols<- c("FILM"  , "STARS" , "RATING", "VOTES" )

# create a variable for column descriptions
desc_cols <- c('Name of the movie', 'Number of stars presented on Fandango.com' , 'Actual average score the movie obtained' ,'number of people who had reviewed the film')

# add columns to dataframe desc
desc$colname <- cols
desc$desc_cols <- desc_cols

# create a table using kable from knitr
knitr::kable(desc, "simple")

```

Summary Statistics

```{r summary-stats, echo = TRUE} 

# get three columns from dataframe
df_new <- highvotes[ , c("FILM", "RATING", "VOTES")] 

#summary statistics
summary(df_new)
summary_df <- summary(df_new)

print(summary_df)
```